The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-26 reviews/disc-ac1.tex
Use different figure numbers in author comment

\begin{document}

\textbf{Authors' response to Referee {\#}1}
\bigskip

% ----------------------------------------------------------------------
\def\referee#1{\bigskip\textcolor{journalname}{\textit{#1}}}

@@

For paper Fig.~9 (temperature difference maps, Fig.~1 in this comment), lapse-rate correction results in smoother temperature difference maps, where effective temperature discrepancies are no longer overshadowed by local topographic anomalies (this comment's Fig.~2). Because temperature differences in this new map are much reduced, we adjusted colour scaling to emphasize smaller values (this comment's Fig.~3).

For paper Fig.~8 (temperature density maps), we now use bilinearly-interpolated temperature maps, rather than the original data (as presented in paper Fig.~2--4). This results in smoother density plots than those presented in the discussion paper (this comment's Fig.~4). In a second step, we apply a lapse-rate correction to project all reanalysis data onto the WorldClim (higher resolution) topography (this comment's Fig.~5). It now becomes clear that much of the discrepancies observed were due to lapse-rate effects.

For consistency, paper Fig.~10 (precipitation density maps) was also updated using bilinearly-interpolated data (this comment's Fig.~6). Note that for all density maps, colour maps were changed to allow for a higher level of detail.

@@

% ----------------------------------------------------------------------

@@

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+tcdc}
    \caption{Summer temperature difference maps, as in paper Fig.~9.}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+lr+tcdc}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$.}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+lr}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$ and an updated colour mapping.}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap}
    \caption{Summer temperature density maps, after bilinear interpolation.}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap+lr}
    \caption{Summer temperature density maps, after bilinear interpolation and lapse-rate correction.}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-precheatmap}
    \caption{Winter precipitation density maps, after bilinear interpolation.}
\end{figure}

>>>>

\begin{document}
\textbf{Authors' response to Referee {\#}1}
\bigskip

% ----------------------------------------------------------------------
% Interactive comment text begins
% ----------------------------------------------------------------------

\renewcommand\thefigure{AC\arabic{figure}}
\def\referee#1{\bigskip\textcolor{journalname}{\textit{#1}}}

@@

For paper Fig.~9 (temperature difference maps, Fig.~AC1), lapse-rate correction results in smoother temperature difference maps, where effective temperature discrepancies are no longer overshadowed by local topographic anomalies (Fig.~AC2). Because temperature differences in this new map are much reduced, we adjusted colour scaling to emphasize smaller values (Fig.~AC3).

For paper Fig.~8 (temperature density maps), we now use bilinearly-interpolated temperature maps, rather than the original data (as presented in Fig.~2--4). This results in smoother density plots than those presented in the discussion paper (Fig.~AC4). In a second step, we apply a lapse-rate correction to project all reanalysis data onto the WorldClim (higher resolution) topography (Fig.~AC5). It now becomes clear that much of the discrepancies observed were due to lapse-rate effects.

For consistency, paper Fig.~10 (precipitation density maps) was also updated using bilinearly-interpolated data (this comment's Fig.~AC6). Note that for all density maps, colour maps were changed to allow for a higher level of detail.

@@

% ----------------------------------------------------------------------
% Interactive comment text ends
% ----------------------------------------------------------------------

@@

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+tcdc}
    \caption{Summer temperature difference maps, as in paper Fig.~9.}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+lr+tcdc}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$.}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+lr}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$ and an updated colour mapping.}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap}
    \caption{Summer temperature density maps, after bilinear interpolation.}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap+lr}
    \caption{Summer temperature density maps, after bilinear interpolation and lapse-rate correction.}
\end{figure}

\begin{figure}
    \center
    \includegraphics[width=70mm]{cordillera-climate-precheatmap}
    \caption{Winter precipitation density maps, after bilinear interpolation.}
\end{figure}
